Summary of cell type ontologies in reference files

### 2024-12-18 analyses/cell-type-consensus/exploratory-notebooks/01-reference-exploration.Rmd
add note about keratinocytes

The PanglaoDB cell types seem to be more specific than the ones present in Blueprint Encode, similar to the observation with neurons.
We should keep epithelial cell.

@@

- Pairs should not have more than 1 LCA, with the exception of the matches that have the label hematopoietic precursor cell. 
- The LCA should have equal to or less than 170 total descendants. 
- We whould include the term for `neuron` and `epithelial cell` even though they do not pass the threshold for number of descendants. 
- Terms that are too broad should be removed. 
This includes: `lining cell`, `blood cell`, `progenitor cell`, `bone cell`, and `supporting cell`

>>>>

The PanglaoDB cell types seem to be more specific than the ones present in Blueprint Encode, similar to the observation with neurons.
We should keep epithelial cell in the cases where the Blueprint Encode annotation is `Epithelial cells` but not when it is `Keratinocytes`.

@@

- Pairs should not have more than 1 LCA, with the exception of the matches that have the label hematopoietic precursor cell. 
- The LCA should have equal to or less than 170 total descendants. 
- We should include the term for `neuron` and `epithelial cell` even though they do not pass the threshold for number of descendants. 
However, `epithelial cell` should only be included if the Blueprint Encode name is `Epithelial cells` and _not_ `Keratinocytes`.
- Terms that are too broad should be removed. 
This includes: `lining cell`, `blood cell`, `progenitor cell`, `bone cell`, and `supporting cell`
